### 2015-05-24 docs/report/micro_benchmarks.tex

\begin{description}
\item[First] Be able to evalute the time it takes to perform the operation multiple times (a single execution could either be too small or an outlier and the measurement could have too much variance/error).
\item[Second] Allow JIT optimizations to kick in.
\end{description}

@@

\subsection{A small example\protect\footnote{The example is based on \cite{mraleph-bc}.}}
Let's assume that we want to profile the following function:
\begin{lstlisting}[caption=Function to benchmark]
function between(a, b, c){
  return a <= b <= c;
}
\end{lstlisting}

@@

\textbf{Machine 2}
\begin{itemize}
  \item Mac Book Air
  \item Intel Core i5 1.8GHz
  \item 4 GB RAM DDR3 1600 MHz
  \item SSD 128 GB
  \item Chrome 43.0.2357
\end{itemize}

>>>>

\begin{description}
\item[First] Be able to evaluate the time it takes to perform the operation multiple times (a single execution could either be too small or an outlier and the measurement could have too much variance/error).
\item[Second] Allow JIT optimizations to kick in.
\end{description}

@@

\subsection{A small example\protect\footnote{The example is based on \cite{mraleph-bc}.}}
Let's assume that we want to profile the following function:
\begin{lstlisting}[caption=Function to benchmark]
function between(a, b, c){
  return a <= b && b <= c;
}
\end{lstlisting}

@@

\textbf{Machine 2}
\begin{itemize}
  \item Mac Book Air
  \item Intel Core i5 1.8GHz
  \item 4 GB RAM DDR3 1600 MHz
  \item SSD 128 GB
  \item Chrome 40.0.2214
  \item Firefox Nightly 41.0a1
\end{itemize}
